---
title: "Introduction to Test R Package"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is meant to provide a brief introduction to the package functions.

## fars_read

This is a helper function that reads the data.

```{r echo=TRUE}

fars_read <- function(filename) {
  if(!file.exists(filename))
    stop("file '", filename, "' does not exist")
  data <- suppressMessages({
    read_csv(filename, progress = FALSE)
  })
  tbl_df(data)
}

```


## make_filename

This is a helper function that creates a filename that matches the integer year value specified by the user.

```{r, echo=TRUE}

make_filename <- function(year) {
  year <- as.integer(year)
  sprintf("accident_%d.csv.bz2", year)
}

```

## fars_read_years

This fuction reads the data which is to be summarized and visualized.

```{r, echo=TRUE}

fars_read_years <- function(years) {

  lapply(years, function(year) {
    file <- make_filename(year)
    tryCatch({
      dat <- fars_read(file)
      mutate(dat, year = year) %>%
        select(MONTH, year)
    }, error = function(e) {
      warning("invalid year: ", year)
      return(NULL)
    })
  })
}

```

## fars_summarize_years

This function applies summary functions to the dataset utilizing dplyr functionality.

```{r, echo=TRUE}

fars_summarize_years <- function(years) {

  dat_list <- fars_read_years(years) %>%
    bind_rows(dat_list) %>%
    group_by(year, MONTH) %>%
    summarize(n = n()) %>%
    spread(year, n)
}

```

## fars_map_state

```{r, echo=FALSE}

fars_map_state <- function(state.num, year) {

  globalVariables(c("STATE"))

  filename <- make_filename(year)
  data <- fars_read(filename)
  state.num <- as.integer(state.num)

  if(!(state.num %in% unique(data$STATE)))
    stop("invalid STATE number: ", state.num)
  data.sub <- filter(data, STATE == state.num)
  if(nrow(data.sub) == 0L) {
    message("no accidents to plot")
    return(invisible(NULL))
  }
  is.na(data.sub$LONGITUD) <- data.sub$LONGITUD > 900
  is.na(data.sub$LATITUDE) <- data.sub$LATITUDE > 90
  with(data.sub, {
    map("state", ylim = range(LATITUDE, na.rm = TRUE),
              xlim = range(LONGITUD, na.rm = TRUE))
    points(LONGITUD, LATITUDE, pch = 46)
  })
}

```
